---
title: "Trust in political institutions and support for authoritarianism in Latin American students: Does civic knowledge make a difference?"
author: "Juan Carlos Castillo, Daniel Miranda, Catalina Miranda & José Conejeros"
date: '`r format(Sys.time(), "%d/%m/%Y")`'
output: 
  html_document:
    theme: cosmo
    highlight: tango
    code_folding: hide
    toc: yes
    toc_float: true
---

Below are descriptive and correlational statistics with data from to the International Civic and Citizenship Education Study (ICCS) 2009 and 2016, in which six (Chile, Mexico, Colombia, Paraguay, Guatemala, and the Dominican Republic) and five (Chile, Mexico, Colombia, Peru, and the Dominican Republic) Latin American countries participated, respectively. The following sections are presented: change in support for dictatorship, support for Dictatorship on civic knowledge and support for Dictatorship on institutional trust

```{r global options, warning=FALSE, cache=FALSE, include=FALSE, results="asis"}
rm(list = ls()) #limpiar la memoria
#Desactivar notación científica
options(scipen=999)
#Paquetes
library(knitr)
library(DT)
library(plyr)
library(dplyr)
library(haven)
library(texreg) 
library(xtable) 
library(kableExtra) 
library(ggplot2)
library(psych)
library(purrr)
library(tidyr)
library(sjmisc)
library(Hmisc)
library(reshape)
library(VIM)
library(stringr)
library(skimr)
library(lme4)
library(broom)
library(survey)
library(srvyr)
#Global
opts_chunk$set(echo = FALSE,
	             cache = FALSE,
               prompt = FALSE,       
               tidy = FALSE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 1000)
options(max.print = 1000)
```

# Data Frames

+ ICCS 2009: Chile, Mexico, Colombia, Paraguay, Guatemala, and the Dominican Republic

```{r iccs09, warning=FALSE, cache=FALSE, results="asis"}
#ICCS 2009: Latinamerica module, student questionnaire
#Chile
chile09 <-  as.data.frame(read_sas("ICCS2009_IDB_SAS/Data_G8/islchlc2.sas7bdat"))
#México
mexico09 <-  as.data.frame(read_sas("ICCS2009_IDB_SAS/Data_G8/islmexc2.sas7bdat"))
#Colombia
colombia09 <- as.data.frame(read_sas("ICCS2009_IDB_SAS/Data_G8/islcolc2.sas7bdat"))
#Paraguay
paraguay09 <- as.data.frame(read_sas("ICCS2009_IDB_SAS/Data_G8/islpryc2.sas7bdat"))
#Guatemala
guatemala09 <- as.data.frame(read_sas("ICCS2009_IDB_SAS/Data_G8/islgtmc2.sas7bdat"))
#República Dominicana
dom09 <- as.data.frame(read_sas("ICCS2009_IDB_SAS/Data_G8/isldomc2.sas7bdat"))
#Append: all obervations preserve
iccs09 <- rbind(chile09, mexico09, colombia09, paraguay09, guatemala09, dom09)
#class(iccs09)
#dim(iccs09)
#head(iccs09)
#str(iccs09)
#names(iccs09)
#dplyr::glimpse(iccs09) # ver estructura general
#ICCS 2009
save(iccs09, file = "BBDD_ICCS/ICCS09.Rdata")
```

+ ICCS 2016: Chile, Mexico, Colombia, Peru, and the Dominican Republic

```{r iccs16, warning=FALSE, cache=FALSE, results="asis"}
#ICCS 2016: Latinamerica module, student questionnaire
#Chile
chile16 <-  as.data.frame(read_sas("ICCS2016_IDB_SAS/Data/islchlc3.sas7bdat"))
#México
mexico16 <-  as.data.frame(read_sas("ICCS2016_IDB_SAS/Data/islmexc3.sas7bdat"))
#Colombia
colombia16 <- as.data.frame(read_sas("ICCS2016_IDB_SAS/Data/islcolc3.sas7bdat"))
#República Dominicana
dom16 <- as.data.frame(read_sas("ICCS2016_IDB_SAS/Data/isldomc3.sas7bdat"))
#Perú
peru16 <- as.data.frame(read_sas("ICCS2016_IDB_SAS/Data/islperc3.sas7bdat"))
#Append: all obervations preserve
iccs16 <- rbind(chile16, mexico16, colombia16, dom16, peru16)
#class(iccs16)
#dim(iccs16)
#head(iccs16)
#str(iccs116)
#names(iccs16)
#dplyr::glimpse(iccs16) # ver estructura general
#ICCS 2016
save(iccs16, file = "BBDD_ICCS/ICCS16.Rdata")
#Load Data
load("BBDD_ICCS/ICCS09.Rdata") #29896 obs - 128 vars
load("BBDD_ICCS/ICCS16.Rdata") #25319 obs - 168 vars
#skim(iccs09)
#skim(iccs16)
```

## Process Data

+ Process General Databases ICCS 2009 and ICCS 2016

```{r process, echo=TRUE, eval=TRUE}
#Chile 2016
chi16= chile16 %>%
    rename_all(tolower) %>%
    dplyr::mutate(time="2015") %>%
    dplyr::mutate (gob1= 5 - ls3g01a)%>% #invertidos
    dplyr::mutate (gob2= 5 - ls3g01b)%>%
    dplyr::mutate (gob3= 5 - ls3g01c)%>%
    dplyr::mutate (gob4= 5 - ls3g01d)%>%
    dplyr::mutate (gob5= 5 - ls3g01e)%>%
    dplyr::mutate (gob6= 5 - ls3g01f)%>%
    dplyr::mutate (dicta1= 5 - ls3g02d)%>%
    dplyr::mutate (dicta2= 5 - ls3g02e)%>%
    dplyr::select(country,totwgts, jkzones, jkreps, time, gob1, gob2, gob3, gob4, gob5, gob6, dicta1, dicta2) 

#Chile 2009
chi09= chile09 %>%
      rename_all(tolower) %>%
      dplyr::mutate(time="2008") %>%
      dplyr::mutate (gob1= 5 - ls2p02a)%>% #invertidos
      dplyr::mutate (gob2= 5 - ls2p02b)%>%
      dplyr::mutate (gob3= 5 - ls2p02c)%>%
      dplyr::mutate (gob4= 5 - ls2p02d)%>%
      dplyr::mutate (gob5= 5 - ls2p02e)%>%
      dplyr::mutate (gob6= 5 - ls2p02f)%>%
      dplyr::mutate (dicta1= 5 - ls2p03d)%>%
      dplyr::mutate (dicta2= 5 - ls2p03e)%>%
      dplyr::select(country, totwgts, jkzones, jkreps, time, gob1, gob2, gob3, gob4, gob5, gob6, dicta1, dicta2) 
    
mergeiccs=full_join(chi16, chi09)
```

+ Replication international analisys

```{r process, echo=TRUE, eval=TRUE}
    mergesvy <-  mergeiccs %>%
    filter(country=="CHL") %>%
    as_survey_design(
    strata = jkzones, 
    weights = totwgts, 
    ids = jkreps, 
    nest = TRUE)

    # frequency table via taylor series linearization
    table_freq_01 <- mergesvy %>%
    dplyr::group_by(time, dicta1) %>%
    summarize(proportion = survey_mean( , na.rm=TRUE))
    #help(srvyr)
      
```


## Sample 

+ All observations


```{r sample, echo=TRUE, eval=TRUE}
#Data frames with all variables
#2009
dict09 = iccs09 %>%
  mutate(time          = 2009) %>%
  mutate(country       = COUNTRY) %>%
  mutate(idcountry     = IDCNTRY) %>%
  mutate(idschool       = IDSCHOOL) %>%
  mutate(idstudent     = IDSTUD) %>%
  mutate(idstudent = (time*1000000000000 + idcountry*100000000 + idstudent)) %>% #NEW IDSTUDENT
  mutate(dict_safety   = 5-LS2P03D) %>% #DICTATORSHIPS ARE JUSTIFIED WHEN THEY BRING ORDER AND SAFETY
  mutate(dict_benefits = 5-LS2P03E) %>% #DICTATORSHIPS ARE JUSTIFIED WHEN THEY BRING ECONOMIC BENEFITS
  mutate(dict          = (dict_safety + dict_benefits)/2) %>% #MEAN DIC
  mutate(pv1civ        = PV1CIV) %>%
  mutate(pv2civ        = PV2CIV) %>%
  mutate(pv3civ        = PV3CIV) %>%
  mutate(pv4civ        = PV4CIV) %>%
  mutate(pv5civ        = PV5CIV) %>%
  mutate(civic_knowledge = (pv1civ + pv2civ + pv3civ + pv4civ + pv5civ)/5) %>% #MEAN CIVIC KNOWLEDGE 
  mutate(s_intrust       = INTRUST) %>% #TRUST IN CIVIC INSTITUTIONS 
  mutate(s_opdisc        = OPDISC) %>%  #OPENNESS IN CLASS DISCUSSION
  mutate(s_hisced        = HISCED) %>%  #HIGHEST PARENTAL EDUCATIONAL LEVEL 
  mutate(univ            = ifelse(s_hisced>3, 1, 0)) %>% #UNIVERSITARY PARENTS
  mutate(s_hisei         = HISEI) %>%   #PARENT'S HIGHEST OCCUPATIONAL STATUS
  mutate(s_homelit       = HOMELIT) %>% #HOME LITERACY
  mutate(s_gender        = SGENDER) %>% #GENDER OF STUDENT
  mutate(s_citcon        = CITCON) %>%  #CONVENTIONAL CITIZENSHIP
  mutate(s_citsoc        = CITSOC) %>%  #SOCIAL MOVEMENT REL. CITIZENSHIP
  mutate(s_citeff        = CITEFF) %>%  #CITIZENSHIP SELF-EFFICACY 
  mutate(s_cntatt        = ATTCNT) %>%  #ATTITUDES TOWARDS OWN COUNTRY 
  mutate(s_geneql        = GENEQL) %>%  #ATTITUDES TOWARDS GENDER EQUALITY
  mutate(s_ethrght       = ETHRGHT) %>% #EQUAL RIGHTS FOR ALL ETHNIC GROUPS 
  mutate(l_attviol       = ATTVIOL) %>% #ATTITUDES: USE OF VIOLENCE 
  mutate(l_attdiv        = ATTDIFF) %>% #ATTITUDES: NEIGHBOURHOOD DIVERSITY
  mutate(l_autgov        = AUTGOV) %>%  #AUTHORITARIANISM IN GOVERNMENT 
  mutate(l_attcorr       = ATTCORR) %>% #CORRUPT PRACTICES IN GOVERNMENT
  mutate(l_dislaw        = DISLAW) %>%  #ATTITUDES: DISOBEYING THE LAW
  mutate(l_empclas       = EMPATH) %>%  #EMPATHY TOWARDS CLASSMATES
  mutate(s_poldisc       = POLDISC) %>% #DISCUSSION OF POL. AND SOC. ISSUES
  #TRUST
  mutate(nac_gob         = IS2P27A) %>% #TRUST INSTITUTIONS-NATIONAL GOVERNMENT  
  mutate(local_gob     = IS2P27B) %>% #TRUST INSTITUTIONS-LOCAL GOVERNMENT 
  mutate(courts        = IS2P27C) %>% #TRUST INSTITUTIONS-COURTS
  mutate(police        = IS2P27D) %>% #TRUST INSTITUTIONS-POLICE 
  mutate(pol_parties   = IS2P27E) %>% #TRUST INSTITUTIONS-POLITICAL PARTIES
  mutate(parliament    = IS2P27F) %>% #TRUST INSTITUTIONS-PARLIAMENT
  mutate(media         = IS2P27G) %>% #TRUST INSTITUTIONS-MEDIA
  mutate(ffaa          = IS2P27H) %>% #TRUST INSTITUTIONS-FFAA 
  mutate(school        = IS2P27I) %>% #TRUST INSTITUTIONS-SCHOOL
  mutate(unit_nations  = IS2P27J) %>% #TRUST INSTITUTIONS-UNITED NATIONS 
  mutate(people        = IS2P27K) %>% #TRUST INSTITUTIONS-PEOPLE
  #WEITHINGS
  mutate(totwgts       = TOTWGTS) %>%   #FINAL STUDENT WEIGHT
  mutate(wgtfac1       = WGTFAC1) %>%   #SCHOOL BASE WEIGHT
  mutate(wgtadj1s      = WGTADJ1S) %>%  #SCHOOL WEIGHT ADJUSTMENT-STUDENT STUDY
  mutate(wgtfac2s      = WGTFAC2S) %>%  #CLASS WEIGHT FACTOR
  mutate(wgtadj2s      = WGTADJ2S) %>%  #CLASS WEIGHT ADJUSTMENT
  mutate(wgtadj3s      = WGTADJ3S) %>%  #STUDENT WEIGHT ADJUSTMENT
  mutate(jkzones       = JKZONES) %>%   #JACKKNIFE ZONE - STUDENT STUDY
  mutate(jkreps        = JKREPS)  %>%  #JACKKNIFE REPLICATE CODE
  select(411:463)
  
#2016  
dict16 = iccs16 %>%
  mutate(time            = 2016) %>%
  mutate(country         = COUNTRY) %>%
  mutate(idcountry       = IDCNTRY) %>%
  mutate(idschool        = IDSCHOOL) %>%
  mutate(idstudent       = IDSTUD) %>%
  mutate(idstudent       = (time*100000000000 + idcountry*100000000 + idstudent)) %>% #NEW IDSTUDENT
  mutate(dict_safety     = 5-LS3G02D) %>% #DICTATORSHIPS ARE JUSTIFIED WHEN THEY BRING ORDER AND SAFETY
  mutate(dict_benefits   = 5-LS3G02E) %>% #DICTATORSHIPS ARE JUSTIFIED WHEN THEY BRING ECONOMIC BENEFITS
  mutate(dict            = (dict_safety + dict_benefits)/2) %>% #MEAN DIC
  mutate(pv1civ          = PV1CIV) %>%
  mutate(pv2civ          = PV2CIV) %>%
  mutate(pv3civ          = PV3CIV) %>%
  mutate(pv4civ          = PV4CIV) %>%
  mutate(pv5civ          = PV5CIV) %>%
  mutate(civic_knowledge = (pv1civ + pv2civ + pv3civ + pv4civ + pv5civ)/5) %>% #MEAN CIVIC KNOWLEDGE 
  mutate(s_intrust       = S_INTRUST) %>% #TRUST IN CIVIC INSTITUTIONS 
  mutate(s_opdisc        = S_OPDISC) %>%  #OPENNESS IN CLASS DISCUSSION
  mutate(s_hisced        = S_HISCED) %>%  #HIGHEST PARENTAL EDUCATIONAL LEVEL 
  mutate(univ            = ifelse(s_hisced>3, 1, 0)) %>% #UNIVERSITARY PARENTS
  mutate(s_hisei         = S_HISEI) %>%   #PARENT'S HIGHEST OCCUPATIONAL STATUS
  mutate(s_homelit       = S_HOMLIT) %>%  #HOME LITERACY
  mutate(s_gender        = S_GENDER) %>%  #GENDER OF STUDENT
  mutate(s_citcon        = S_CITCON) %>%  #CONVENTIONAL CITIZENSHIP
  mutate(s_citsoc        = S_CITSOC) %>%  #SOCIAL MOVEMENT REL. CITIZENSHIP
  mutate(s_citeff        = S_CITEFF) %>%  #CITIZENSHIP SELF-EFFICACY 
  mutate(s_cntatt        = S_CNTATT) %>%  #ATTITUDES TOWARDS OWN COUNTRY 
  mutate(s_geneql        = S_GENEQL) %>%  #ATTITUDES TOWARDS GENDER EQUALITY
  mutate(s_ethrght       = S_ETHRGHT) %>% #EQUAL RIGHTS FOR ALL ETHNIC GROUPS 
  mutate(l_attviol       = L_ATTVIOL) %>% #ATTITUDES: USE OF VIOLENCE 
  mutate(l_attdiv        = L_ATTDIV) %>%  #ATTITUDES: NEIGHBOURHOOD DIVERSITY
  mutate(l_autgov        = L_AUTGOV) %>%  #AUTHORITARIANISM IN GOVERNMENT 
  mutate(l_attcorr       = L_ATTCORR) %>% #CORRUPT PRACTICES IN GOVERNMENT
  mutate(l_dislaw        = L_DISLAW) %>%  #ATTITUDES: DISOBEYING THE LAW
  mutate(l_empclas       = L_EMPCLAS) %>% #EMPATHY TOWARDS CLASSMATES
  mutate(s_poldisc       = S_POLDISC) %>% #DISCUSSION OF POL. AND SOC. ISSUES  
  #TRUST
  mutate(nac_gob         = IS3G26A) %>%   #TRUST INSTITUTIONS-NATIONAL GOVERNMENT 
  mutate(local_gob       = IS3G26B) %>%   #TRUST INSTITUTIONS-LOCAL GOVERNMENT 
  mutate(courts          = IS3G26C) %>%   #TRUST INSTITUTIONS-COURTS
  mutate(police          = IS3G26D) %>%   #TRUST INSTITUTIONS-POLICE
  mutate(pol_parties     = IS3G26E) %>%   #TRUST INSTITUTIONS-POLITICAL PARTIES
  mutate(parliament      = IS3G26F) %>%   #TRUST INSTITUTIONS-PARLIAMENT
  mutate(media           = IS3G26G) %>%   #TRUST INSTITUTIONS-MEDIA
  mutate(ffaa            = IS3G26I) %>%   #TRUST INSTITUTIONS-FFAA
  mutate(school          = IS3G26J) %>%   #TRUST INSTITUTIONS-SCHOOL
  mutate(unit_nations    = IS3G26K) %>%   #TRUST INSTITUTIONS-UNITED NATIONS
  mutate(people          = IS3G26L) %>%   #TRUST INSTITUTIONS-PEOPLE
  #WEITHINGS
  mutate(totwgts         = TOTWGTS) %>%   #FINAL STUDENT WEIGHT
  mutate(wgtfac1         = WGTFAC1) %>%   #SCHOOL BASE WEIGHT
  mutate(wgtadj1s        = WGTADJ1S) %>%  #SCHOOL WEIGHT ADJUSTMENT-STUDENT STUDY
  mutate(wgtfac2s        = WGTFAC2S) %>%  #CLASS WEIGHT FACTOR
  mutate(wgtadj2s        = WGTADJ2S) %>%  #CLASS WEIGHT ADJUSTMENT
  mutate(wgtadj3s        = WGTADJ3S) %>%  #STUDENT WEIGHT ADJUSTMENT
  mutate(jkzones         = JKZONES)  %>%  #JACKKNIFE ZONE - STUDENT STUDY
  mutate(jkreps          = JKREPS)  %>%  #JACKKNIFE REPLICATE CODE
  select(519:571)

#Merge data
dict <- rbind(dict09, dict16)
#All observations with complete row data
dict2 <- dict[complete.cases(dict),]
#Number observations
dict_count <- dict %>% 
  group_by(time, country) %>%
  dplyr::summarise(N=n()) %>%
  mutate(Prop. = N / sum(N))  %>%
  arrange(country)
#Table
kable(dict_count, align = c("cccc"), 
      col.names = c("Year","Country", "Prop.", "N"),
      caption = "Sample with all observations", format="html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

+ Missing Value delete

```{r sample without missing, echo=TRUE, eval=TRUE}
#Number observations delete missing values
dict_count2 <- dict2 %>% 
  group_by(time, country) %>%
  dplyr::summarise(N=n(), Prop. = (n()/nrow(dict2)))  %>%
  arrange(country)
#Table  
kable(dict_count2,  caption = "Sample without missing", format="html",
      col.names = c("Year","Country", "Prop.", "N")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


# Change in support for dictatorship

+ Dictatorships are justified when they bring economic benefits 2016: LS2P03E - LS3G02E

```{r dictatorship, echo=TRUE, eval=TRUE}
#Dictatorships are justified when they bring economic benefits 2016: LS2P03E - LS3G02E
bar_civic <- ggplot(subset(dict, !is.na(dict_benefits)), aes(as.factor(dict_benefits), group = country)) +  
  geom_bar(aes(y = ..prop.., group = country)) +
  geom_text(aes(y= ..prop.. , label = scales::percent(..prop..)), stat= "count", vjust = -0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  facet_grid(country ~ time) + 
  ggtitle("Dictatorship are justified when bring economic benefits") +
  scale_x_discrete(labels = c("Very Disagree", "Disagree", "Agree", "Very Agree")) + 
  labs(x = "Agreement", y = "%") 
bar_civic 

bar_civic <- ggplot(dict, aes(as.factor(dict_benefits), group = country)) +  
  geom_bar(aes(y = ..prop.., group = country), na.rm = TRUE) +
  geom_text(aes(y= ..prop.. , label = scales::percent(..prop..)), stat= "count", vjust = -0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  facet_grid(country ~ time) + 
  ggtitle("Dictatorship are justified when bring economic benefits (include missing)") +
  scale_x_discrete(labels = c("Very Disagree", "Disagree", "Agree", "Very Agree")) + 
  labs(x = "Agreement", y = "%") 
bar_civic 
```

+ Dictatorships are justified when they bring order and safety 2009: LS2P03D - LS3G02D

```{r dictatorship2, echo=TRUE, eval=TRUE}
#Dictatorships are justified when they bring order and safety 2009: LS2P03D - LS3G02D
bar_civic <- ggplot(subset(dict, !is.na(dict_safety)), aes(as.factor(dict_safety), group = country)) +  
  geom_bar(aes(y = ..prop.., group = country)) +
  geom_text(aes(y= ..prop.. , label = scales::percent(..prop..)), stat= "count", vjust = -0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  facet_grid(country ~ time) + 
  ggtitle("Dictatorship are justified when bring order and security") +
  scale_x_discrete(labels = c("Very Disagree", "Disagree", "Agree", "Very Agree")) + 
  labs(x = "Agreement", y = "%") 
bar_civic 

bar_civic <- ggplot(dict, aes(as.factor(dict_safety), group = country)) +  
  geom_bar(aes(y = ..prop.., group = country), na.rm = TRUE) +
  geom_text(aes(y= ..prop.. , label = scales::percent(..prop..)), stat= "count", vjust = -0.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  facet_grid(country ~ time) + 
  ggtitle("Dictatorship are justified when bring order and security (include missing)") +
  scale_x_discrete(labels = c("Very Disagree", "Disagree", "Agree", "Very Agree")) + 
  labs(x = "Agreement", y = "%") 
bar_civic 
```

# Support for Dictatorship and civic knowledge

+ Civic knowledge proxy: Mean to PV1CIV, PV2CIV, PV3CIV, PV4CIV, PV5CIV. 

```{r Civic Knowledge, echo=TRUE, eval=TRUE}
#Proxy Civic Knowledge
civic_country_mean09 <- dict %>% filter(time==2009)  %>% group_by(country) %>%
  dplyr::summarise(mean=mean(civic_knowledge),sd=sd(civic_knowledge),n=n()) %>%
  dplyr::mutate(se=sd/sqrt(n)) %>%
  mutate (time=2009)

civic_country_mean16 <- dict %>% filter(time==2016)  %>% group_by(country) %>%  
  dplyr::summarise(mean=mean(civic_knowledge),sd=sd(civic_knowledge),n=n()) %>%
  dplyr::mutate(se=sd/sqrt(n)) %>%
  mutate (time=2016) 

civic_country_mean <- merge(civic_country_mean09, civic_country_mean16, all = T)

kable(civic_country_mean, align = c("cccccc"), caption = "Mean Civic Knowledge") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Graphs Bar
#All
civic_know <- ggplot(civic_country_mean, aes(reorder(to_label(country), -mean),mean), group = time)
civic_know <- civic_know +  geom_bar(stat = "summary") +
  facet_grid(~ time) + 
  geom_text(aes(label = format(mean, digits = 2), vjust=0.3, hjust=-0.2), size=2, colour="black") +
  coord_flip() +
  theme(axis.text=element_text(size=5,face="bold"),
        axis.title=element_text(size=10,face="bold")) + 
  labs(x="Country", y="Civic Knowledge")
civic_know

#Boxplot 
box_civic = ggplot(dict, aes(reorder(to_label(country), -civic_knowledge), civic_knowledge), group = time) 
box_civic + geom_boxplot() +  
  facet_grid(~ time) + 
  coord_flip() + 
  theme(axis.text=element_text(size=5),
        axis.title=element_text(size=10,face="bold")) + 
  labs(x=" ", y="Civic Knowledge")
```

## Latin American 2009-2016: Dictatorship and civic knowledge

+ Dictatorships are justified when they bring economic benefits and civic knowledge

```{r Civic Knowledge and Dictatorship1, echo=TRUE, eval=TRUE}
#Dictatorships are justified when they bring economic benefits 
scatter <- ggplot(dict, aes(civic_knowledge, dict_benefits, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ time) +
    labs(x = "Civic knowledge", y = "Support to dictatorship (economic benefits)", colour = "country") 
```

+ Dictatorships are justified when they bring order and safety and civic knowledge

```{r Civic Knowledge and Dictatorship2, echo=TRUE, eval=TRUE}
#Dictatorships are justified when they bring order and safety 
scatter <- ggplot(dict, aes(civic_knowledge, dict_safety, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ time) +
    labs(x = "Civic knowledge", y = "Support to dictatorship (order and safety)", colour = "country")    
```

+ Dictatorships are justified (means of the previous two) and civic knowledge

```{r Civic Knowledge and Dictatorship3, echo=TRUE, eval=TRUE}
#Dictatorships are justified mean 
scatter <- ggplot(dict, aes(civic_knowledge, dict, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ time) +
    labs(x = "Civic knowledge", y = "Support to dictatorship (mean)", colour = "country")  
```

## Latin American 2009-2016: institutional trust and civic knowledge

```{r Civic Knowledge and institutional trust, echo=TRUE, eval=TRUE}
#Trust in civic institutions and civic knowledge
scatter <- ggplot(dict, aes(civic_knowledge, s_intrust, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ time) +
    labs(x = "Civic knowledge", y = "Trust in civic institutions", colour = "country") 
```

# Support for Dictatorship and institutional trust

## Latin American 2009-2016: Institutional trust

```{r Institutional trust, echo=TRUE, eval=TRUE}
in_trust09 <- dict2 %>% filter(time==2009)  %>% group_by(country) %>%
  dplyr::summarise(mean=mean(s_intrust),sd=sd(s_intrust),n=n()) %>%
  dplyr::mutate(se=sd/sqrt(n)) %>%
  mutate (time=2009)

in_trust16 <- dict2 %>% filter(time==2016)  %>% group_by(country) %>%  
  dplyr::summarise(mean=mean(s_intrust),sd=sd(s_intrust),n=n()) %>%
  dplyr::mutate(se=sd/sqrt(n)) %>%
  mutate (time=2016) 

in_trust_mean <- merge(in_trust09, in_trust16, all = T)

kable(in_trust_mean, align = c("cccccc"), caption = "Mean trust in civic institutions") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Graphs Bar
#All
bar_intrust <- ggplot(in_trust_mean, aes(reorder(to_label(country), mean),mean), group = time)
bar_intrust <- bar_intrust +  geom_bar(stat = "summary") +
  facet_grid(~ time) + 
  geom_text(aes(label = format(mean, digits = 2), vjust=0.3, hjust=-0.2), size=2, colour="black") +
  coord_flip() +
  theme(axis.text=element_text(size=5,face="bold"),
        axis.title=element_text(size=10,face="bold")) + 
  labs(x="Country", y="Trust in civic institutions")
bar_intrust

#Boxplot 
box_intrust = ggplot(dict, aes(reorder(to_label(country), -s_intrust), s_intrust), group = time) 
box_intrust + geom_boxplot() +  
  facet_grid(~ time) + 
  coord_flip() + 
  theme(axis.text=element_text(size=5),
        axis.title=element_text(size=10,face="bold")) + 
  labs(x=" ", y="Trust in civic institutions")

```


## Latin American 2009-2016: Dictatorship and institutional trust

+ Dictatorships are justified when they bring economic benefits and institutional trust

```{r Institutional trust and Dictatorship, echo=TRUE, eval=TRUE}
#Dictatorships are justified when they bring economic benefits 
scatter <- ggplot(dict, aes(s_intrust, dict_benefits, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ time) +
    labs(x = "Trust in civic institutions", y = "Support to dictatorship (economic benefits)", colour = "country") 
    
```


+ Dictatorships are justified when they bring order and safety and institutional trust

```{r Institutional trust and Dictatorship2, echo=TRUE, eval=TRUE}
#Dictatorships are justified when they bring order and safety 
scatter <- ggplot(dict, aes(s_intrust, dict_safety, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ time) +
    labs(x = "Trust in civic institutions", y = "Support to dictatorship (order and safety)", colour = "country")    
```

+ Dictatorships are justified (means of the previous two) and institutional trust

```{r Institutional trust and Dictatorship3, echo=TRUE, eval=TRUE}
#Dictatorships are justified mean 
scatter <- ggplot(dict, aes(s_intrust, dict, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ time) +
    labs(x = "Trust in civic institutions", y = "Support to dictatorship (mean)", colour = "country")     
```


# Regression Model by country (simple)

```{r Institutional trust and Dictatorship Country, echo=TRUE, eval=TRUE, results='asis'}
#Models Chile
ch09= dict %>% filter(country=="CHL" & time==2009) 
mch09 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=ch09)
ch16= dict %>% filter(country=="CHL" & time==2016) 
mch16 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=ch16)

#Models Colombia
col09= dict %>% filter(country=="COL" & time==2009) 
mcol09 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=col09)
col16= dict %>% filter(country=="COL" & time==2016) 
mcol16 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=col16)

#Models República Dominicana
dom09= dict %>% filter(country=="DOM" & time==2009) 
mdom09 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=dom09)
dom16= dict %>% filter(country=="DOM" & time==2016) 
mdom16 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=dom16)

#Models México
mex09= dict %>% filter(country=="MEX" & time==2009) 
mmex09 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=mex09)
mex16= dict %>% filter(country=="MEX" & time==2016) 
mmex16 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=mex16)

#Models Guatemala 2009
gtm09= dict %>% filter(country=="GTM" & time==2009) 
mgtm09 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=gtm09)

#Models Paraguay 2009
pry09= dict %>% filter(country=="PRY" & time==2009) 
mpry09 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=pry09)

#Models Perú 2016
per16= dict %>% filter(country=="PER" & time==2016) 
mper16 = lmer(dict ~ s_intrust + civic_knowledge +  (1 | idschool), weights=totwgts, data=per16)

#Table
library(stargazer)
stargazer(l=list(mch09,mch16,mcol09,mcol16,mdom09, mdom16,mmex09, mmex16), digits = 3, type="html", 
          column.labels=c("Chile 2009", "Chile 2016", "Colombia 2009", "Colombia 2016", "Rep. Dom. 2009", "Rep. Dom. 2016", "Mexico 2009", "Mexico 2016"), 
          covariate.labels =c("Trust institutions", "Civic Knowledge"), 
          dep.var.labels = "Support dictatorship")

stargazer(l=list(mgtm09, mpry09, mper16), digits = 3, type="html", 
          column.labels=c("Guatemala 2009", "Paraguay 2016", "Perú 2009"), 
          covariate.labels =c("Trust institutions", "Civic Knowledge"), 
          dep.var.labels = "Support dictatorship")
```

# Descriptives

+ Dictatorships are justified when they bring economic benefits

```{r describe1, echo=TRUE, eval=TRUE}
tapply(dict$dict_benefits, dict$country, summary)
```

+ Dictatorships are justified when they bring order and security

```{r describe2, echo=TRUE, eval=TRUE}
tapply(dict$dict_safety, dict$country, summary)
```

+ Institutional trust

```{r describe3, echo=TRUE, eval=TRUE}
tapply(dict$s_intrust, dict$country, summary)
```

+ Civic Knowledge

```{r describe4, echo=TRUE, eval=TRUE}
tapply(dict$civic_knowledge, dict$country, summary)
```

# Multilevel Regression Model (simple)

+ Model to 2009

```{r Multilevel, echo=TRUE, eval=TRUE, results='asis'}
#Model to 2009
model09 = lmer(dict ~ 1 + s_intrust + civic_knowledge +  (1 | country), weights=totwgts, data=dict09)
stargazer(model09, digits = 3, type="html", 
          covariate.labels =c("Trust institutions", "Civic Knowledge"), 
          dep.var.labels = "Support dictatorship")
library(sjPlot)
fig09=plot_model(model09, type = "re", 
           show.legend = FALSE,
           show.values = TRUE,
           facet.grid = FALSE,
           y.offset = .4,
           value.offset = .4,
           value.size = 3.5,
           color="darkgray",
           sort.est= 2,
           title = " ",)
fig09
```

+ Model to 2016

```{r Multilevel2, echo=TRUE, eval=TRUE, results='asis'}
#Model to 2016
model16 = lmer(dict ~ 1 + s_intrust + civic_knowledge +  (1 | country), weights=totwgts, data=dict16)
stargazer(model16, digits = 3, type="html", 
          covariate.labels =c("Trust institutions", "Civic Knowledge"), 
          dep.var.labels = "Support dictatorship")

fig16=plot_model(model16, type = "re", 
           show.legend = FALSE,
           show.values = TRUE,
           facet.grid = FALSE,
           y.offset = .4,
           value.offset = .4,
           value.size = 3.5,
           color="darkgray",
           sort.est= 2,
           title = " ",)
fig16
```

