---
title: "Supporting democracy from the school"
subtitle: "A comparison of five Latin American countries"
author: 
keywords: Political Socialization, Anti-democractic values, ICCS 2019-2016.
date: Octubre de 2018
output: html_document
---
  

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(dev = 'jpg')
# remove all previous objects
rm(list = ls()) 
```



```{r , eval=TRUE, results='asis', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
pacman::p_load(knitr, haven, foreing, ggplot2, reshape, plyr, dplyr, readstata13, VIM, stringr, skimr, xaringan, srvyr, lme4, broom, texreg, mediate, psych, MBESS, MplusAutomation)
````


```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE}
##Directorio para imagenes
setwd("C:/Users/DANIEL/Dropbox/MIDEUC/Corruption and trust/figures")

iccs16=read.dta13("C:/Users/DANIEL/Dropbox/GEMR 2019/Data/Merge/ICCS_School_Teachers_Students_Europe_LA.dta", convert.factors = FALSE)

iccs09=read.dta13("C:/Users/DANIEL/Dropbox/mesa educacion ciudadana/IEA studies/ICCS/Internacional/LA_ICCS.dta", convert.factors = FALSE)



#iccs=haven::read_dta("C:/Users/DANIEL/Dropbox/MIDEUC/Corruption and trust/ICCS2016.dta")

## Explorar la base

    #class(iccs)
    #dim(iccs)
    #head(iccs)
    #str(iccs)
    
    #names(iccs09)
    #names(iccs16)
    
    #dplyr::glimpse(iccs09) # ver estructura general
    
    la16= iccs16 %>%
      rename_all(tolower) %>%
      mutate(LA = ifelse(country == "CHL", "LA", ifelse(country == "COL", "LA", ifelse(country == "DOM", "LA", ifelse(country == "MEX", "LA", ifelse(country == "PER", "LA", "NOLA")))))) %>%
      rowwise() %>% 
      dplyr::mutate(study="16") %>%
      dplyr::mutate (dicta1= 5 - ls3g02d)%>%
      dplyr::mutate (dicta2= 5 - ls3g02e)%>%
      dplyr::mutate (dictadura= mean(c(dicta1, dicta2)))%>%
      dplyr::mutate (pituto= is3g22a) %>%
      dplyr::mutate (prensa= is3g22b) %>%
      dplyr::mutate (police= is3g22f) %>%
      dplyr::mutate (cortes= is3g22h) %>%
      dplyr::mutate (dicdum= ifelse(dicta1>2, 1, 0)) %>%
      dplyr::mutate (univ= ifelse(s_hisced>2, 1, 0)) %>%
      dplyr::mutate (civic= mean(c(pv1civ, pv2civ, pv3civ, pv4civ, pv5civ))) %>%
      dplyr::mutate (civic200= (pv1civ /200)) %>%
      dplyr::filter(LA=="LA") %>%
      dplyr::select(idcntry, country, idschool, idstud, totwgts, wgtfac1, wgtadj1s, wgtfac2s, wgtadj2s, wgtadj3s, jkzones, jkreps, pv1civ, pv2civ, pv3civ, pv4civ, pv5civ, civic, s_intrust, s_opdisc, s_hisced, s_hisei, s_homlit, s_gender, s_citcon, s_citsoc, s_citresp, s_citeff, s_cntatt, s_abuse, s_civlrn, s_geneql, s_ethrght, l_attviol, l_attdiv, l_atths, l_autgov, l_attcorr, l_dislaw, l_empclas, study, dicta1, dicta2, dictadura, dicdum, univ, s_poldisc, pituto, prensa, police, cortes, civic200, LA)
    
    #print
    #names(la16)
    #skim(la16)
    #table(la16$ls3g02d, la16$ls3g02e)
    #pacman::p_load(Hmisc)
    #rcorr(la16$ls3g02d, la16$ls3g02b)
################
 #la16 %>% 
      #group_by(study) %>%
      #skimr::skim(c(civic, l_attviol, l_attdiv, l_autgov, l_attcorr, l_dislaw, l_empclas, dictadura, univ, pituto, dicdum))
    
      #la=mergeiccs %>%
      #filter(country=="CHL" | country=="COL" | country=="MEX" | country=="DOM")
    
  #merge4 %>% 
   #   group_by(study) %>%
   #  skimr::skim(c(civic, l_attviol, l_attdiv, l_autgov, l_attcorr, l_dislaw, l_empclas, dictadura, univ, s_poldisc))

#iccsp= corr %>%
#  na.omit() %>%
#  print
````

### 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
    la09= iccs09 %>%
      rowwise() %>%
      dplyr::mutate(study="09") %>%
      dplyr::mutate (civic= mean(c(pv1civ, pv2civ, pv3civ, pv4civ, pv5civ))) %>%
      dplyr::mutate (s_intrust= intrust) %>%
      dplyr::mutate (s_opdisc= opdisc) %>%
      dplyr::mutate (s_hisced= hisced) %>%
      dplyr::mutate (s_hisei= hisei) %>%
      dplyr::mutate (s_homlit= homelit) %>%
      dplyr::mutate (s_gender= sgender) %>%
      dplyr::mutate (s_citcon= citcon) %>%
      dplyr::mutate (s_citsoc= citsoc) %>%
      dplyr::mutate (s_citeff= citeff) %>%
      dplyr::mutate (s_cntatt= attcnt) %>%
      dplyr::mutate (s_geneql= geneql) %>%
      dplyr::mutate (s_ethrght= ethrght) %>%
      dplyr::mutate (l_attviol= attviol) %>%
      dplyr::mutate (l_attdiv= attdiff) %>%
      dplyr::mutate (l_autgov= autgov) %>%
      dplyr::mutate (l_attcorr=attcorr) %>%
      dplyr::mutate (l_dislaw= dislaw) %>%
      dplyr::mutate (l_empclas= empath) %>%
      dplyr::mutate (s_poldisc= poldisc) %>%
      dplyr::mutate (dicta1= 5 - LS2P03D)%>%
      dplyr::mutate (dicta2= 5 - LS2P03E)%>%
      dplyr::mutate (dictadura= mean(c(dicta1, dicta2)))%>%
      dplyr::mutate (univ= ifelse(s_hisced>3, 1, 0)) %>%
      dplyr::select(idcntry, country, idschool, idstud, totwgts, wgtfac1, wgtadj1s, wgtfac2s, wgtadj2s, wgtadj3s, jkzones, jkreps, pv1civ, pv2civ, pv3civ, pv4civ, pv5civ, civic, s_intrust, s_opdisc, s_hisced, s_hisei, s_homlit, s_gender, s_citcon, s_citsoc, s_citeff, s_cntatt, s_geneql, s_ethrght, expagg, l_attviol, l_attdiv, l_autgov, l_attcorr, l_dislaw, l_empclas, study, dicta1, dicta2, dictadura, univ, s_poldisc) 
    
    #print
    #names(la09)  
    #skim(la09)
    
    mergeiccs=full_join(la16, la09)

## crear un objeto con el diseño
    #library(srvyr)
````

## Change in support for dictatorship in Chile.

```{r, echo=TRUE, warning=FALSE}
        mergesvy <-  mergeiccs %>%
        filter(country=="CHL") %>%
        as_survey_design(
        strata = jkzones, 
        weights = totwgts, 
        ids = jkreps, 
        nest = TRUE)

    # frequency table via taylor series linearization
      table_freq_01 <- mergesvy %>%
        dplyr::group_by(study, dicta1) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_01, digits = 4)
      
      df=data.frame(table_freq_01, digits=2)
      #summary(factor(df$proportion))
      
      df= df %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta1, labels=c("Very disagree", "Disagree", "Agree", "Very agree"))) 
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      
      order_chile=ggplot(df, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
         ggtitle("Dictatorship are justified when bring order and security") +
        labs(x = "Response", y = "%") +
        geom_col()
      
      
      #############
      # frequency table via taylor series linearization
      table_freq_02 <- mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_02, digits = 4)
      
      df2=data.frame(table_freq_02, digits=2)
      
      
      mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))

      
      df2= df2 %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta2, labels=c("Very disagree", "Disagree", "Agree", "Very agree")))
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      #
      
      
      econ_chile=ggplot(df2, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
        ggtitle("Dictatorship are justified when bring economic benefits") +
        labs(x = "Response", y = "%") +
        geom_col()
      
    #plotly(p)
    
    #names(mergesvy)
    #str(mergesvy)
    
    #merge= chile %>%
    #  na.omit()
     
    
## Diferencias Autoritarismo de Gobierno
    #res=chile %>%
    # p= group_by(country, study) %>% 
    #  do(model = lmer(dictadura ~ 1 + (1 | idschool),weights=totwgts, data = .))
    
   # ggplotly(p)
    
    #res %>%
    #  tidy(model)
    
    #mod=res %>%
    #  tidy(model)%>%
    #  filter(group=="fixed")
    
    #ggplot(mod, aes(estimate, reorder(country, estimate), color = (study))) +
    #  geom_point(size = 2)+
    #  labs(x = 'Intercepto Apoyo Dictaduta', y = 'País')+
    #geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error), alpha=1/2)
````


```{r , eval=TRUE, echo=TRUE, warning=FALSE, tidy=TRUE} 
print(order_chile)
print(econ_chile)
````


## Change in support for dictatorship in Mexico.

```{r, echo=FALSE, warning=FALSE}
        mergesvy <-  mergeiccs %>%
        filter(country=="MEX") %>%
        as_survey_design(
        strata = jkzones, 
        weights = totwgts, 
        ids = jkreps, 
        nest = TRUE)

    # frequency table via taylor series linearization
      table_freq_01 <- mergesvy %>%
        dplyr::group_by(study, dicta1) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_01, digits = 4)
      
      df=data.frame(table_freq_01, digits=2)
      #summary(factor(df$proportion))
      
      df= df %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta1, labels=c("Very disagree", "Disagree", "Agree", "Very agree"))) 
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      
      order_mex=ggplot(df, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
         ggtitle("Dictatorship are justified when bring order and security") +
        labs(x = "Response", y = "%") +
        geom_col()
      
      
      #############
      # frequency table via taylor series linearization
      table_freq_02 <- mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_02, digits = 4)
      
      df2=data.frame(table_freq_02, digits=2)
      
      
      mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))

      
      df2= df2 %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta2, labels=c("Very disagree", "Disagree", "Agree", "Very agree")))
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      #
      
      
      econ_mex=ggplot(df2, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
        ggtitle("Dictatorship are justified when bring economic benefits") +
        labs(x = "Response", y = "%") +
        geom_col()
      
    #plotly(p)
    
    #names(mergesvy)
    #str(mergesvy)
    
    #merge= chile %>%
    #  na.omit()
     
    
## Diferencias Autoritarismo de Gobierno
    #res=chile %>%
    # p= group_by(country, study) %>% 
    #  do(model = lmer(dictadura ~ 1 + (1 | idschool),weights=totwgts, data = .))
    
   # ggplotly(p)
    
    #res %>%
    #  tidy(model)
    
    #mod=res %>%
    #  tidy(model)%>%
    #  filter(group=="fixed")
    
    #ggplot(mod, aes(estimate, reorder(country, estimate), color = (study))) +
    #  geom_point(size = 2)+
    #  labs(x = 'Intercepto Apoyo Dictaduta', y = 'País')+
    #geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error), alpha=1/2)
````


```{r , eval=TRUE, echo=TRUE, warning=FALSE, tidy=TRUE} 
print(order_mex)
print(econ_mex)
````

## Change in support for dictatorship in Colombia.

```{r, echo=FALSE, warning=FALSE}
        mergesvy <-  mergeiccs %>%
        filter(country=="COL") %>%
        as_survey_design(
        strata = jkzones, 
        weights = totwgts, 
        ids = jkreps, 
        nest = TRUE)

    # frequency table via taylor series linearization
      table_freq_01 <- mergesvy %>%
        dplyr::group_by(study, dicta1) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_01, digits = 4)
      
      df=data.frame(table_freq_01, digits=2)
      #summary(factor(df$proportion))
      
      df= df %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta1, labels=c("Very disagree", "Disagree", "Agree", "Very agree"))) 
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      
      order_col=ggplot(df, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
         ggtitle("Dictatorship are justified when bring order and security") +
        labs(x = "Response", y = "%") +
        geom_col()
      
      
      #############
      # frequency table via taylor series linearization
      table_freq_02 <- mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_02, digits = 4)
      
      df2=data.frame(table_freq_02, digits=2)
      
      
      mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))

      
      df2= df2 %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta2, labels=c("Very disagree", "Disagree", "Agree", "Very agree")))
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      #
      
      
      econ_col=ggplot(df2, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
        ggtitle("Dictatorship are justified when bring economic benefits") +
        labs(x = "Response", y = "%") +
        geom_col()
      
    #plotly(p)
    
    #names(mergesvy)
    #str(mergesvy)
    
    #merge= chile %>%
    #  na.omit()
     
    
## Diferencias Autoritarismo de Gobierno
    #res=chile %>%
    # p= group_by(country, study) %>% 
    #  do(model = lmer(dictadura ~ 1 + (1 | idschool),weights=totwgts, data = .))
    
   # ggplotly(p)
    
    #res %>%
    #  tidy(model)
    
    #mod=res %>%
    #  tidy(model)%>%
    #  filter(group=="fixed")
    
    #ggplot(mod, aes(estimate, reorder(country, estimate), color = (study))) +
    #  geom_point(size = 2)+
    #  labs(x = 'Intercepto Apoyo Dictaduta', y = 'País')+
    #geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error), alpha=1/2)
````


```{r , eval=TRUE, echo=TRUE, warning=FALSE, tidy=TRUE} 
print(order_col)
print(econ_col)
````

## Change in support for dictatorship in Rep. Dominicana.

```{r, echo=FALSE, warning=FALSE}
        mergesvy <-  mergeiccs %>%
        filter(country=="DOM") %>%
        as_survey_design(
        strata = jkzones, 
        weights = totwgts, 
        ids = jkreps, 
        nest = TRUE)

    # frequency table via taylor series linearization
      table_freq_01 <- mergesvy %>%
        dplyr::group_by(study, dicta1) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_01, digits = 4)
      
      df=data.frame(table_freq_01, digits=2)
      #summary(factor(df$proportion))
      
      df= df %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta1, labels=c("Very disagree", "Disagree", "Agree", "Very agree"))) 
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      
      order_gua=ggplot(df, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
         ggtitle("Dictatorship are justified when bring order and security") +
        labs(x = "Response", y = "%") +
        geom_col()
      
      
      #############
      # frequency table via taylor series linearization
      table_freq_02 <- mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))
      #help(srvyr)
      
      # display table only
      #knitr::kable(table_freq_02, digits = 4)
      
      df2=data.frame(table_freq_02, digits=2)
      
      
      mergesvy %>%
        dplyr::group_by(study, dicta2) %>%
        summarize(proportion = survey_mean(,na.rm=TRUE))

      
      df2= df2 %>%
        mutate(perc = proportion * 100) %>%
        mutate(p=round(perc, 2)) %>%
        mutate(label=factor(dicta2, labels=c("Very disagree", "Disagree", "Agree", "Very agree")))
      
      #df <- data.frame(trt = c("a", "b", "c", "d"), outcome = c(0.136, 0.212, 0.477, 0.176), study=c(09, 09, 09, 09))
      #
      
      
      econ_gua=ggplot(df2, aes(label, proportion)) +
        facet_wrap(~ study) +
         geom_text(aes(label = p), position = position_dodge(0.3), vjust=-0.1)+
        theme(axis.text.x = element_text(angle =45, hjust = 1)) +
        ggtitle("Dictatorship are justified when bring economic benefits") +
        labs(x = "Response", y = "%") +
        geom_col()
      
    #plotly(p)
    
    #names(mergesvy)
    #str(mergesvy)
    
    #merge= chile %>%
    #  na.omit()
     
    
## Diferencias Autoritarismo de Gobierno
    #res=chile %>%
    # p= group_by(country, study) %>% 
    #  do(model = lmer(dictadura ~ 1 + (1 | idschool),weights=totwgts, data = .))
    
   # ggplotly(p)
    
    #res %>%
    #  tidy(model)
    
    #mod=res %>%
    #  tidy(model)%>%
    #  filter(group=="fixed")
    
    #ggplot(mod, aes(estimate, reorder(country, estimate), color = (study))) +
    #  geom_point(size = 2)+
    #  labs(x = 'Intercepto Apoyo Dictaduta', y = 'País')+
    #geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error), alpha=1/2)
````


```{r , eval=TRUE, echo=TRUE, warning=FALSE, tidy=TRUE} 
print(order_gua)
print(econ_gua)
````


## Support for Dictatorship on civic knowledge

```{r , eval=TRUE, echo=TRUE, warning=FALSE, tidy=TRUE}    
    #ggplot(la16, aes(x=study, y=dictadura)) +
    #  facet_wrap(~ country) +
    #  stat_summary(fun.y = mean, geom = "bar", fill = "White", colour = "Black")

    scatter <- ggplot(la16, aes(pv1civ, dictadura, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ study) +
    labs(x = "Civic knowledge", y = "Support to dictatorship", colour = "country") 
````


## Support for Dictatorship on institutional trust

```{r , eval=TRUE, echo=TRUE, warning=FALSE, tidy=TRUE}    
    #ggplot(la16, aes(x=study, y=dictadura)) +
    #  facet_wrap(~ country) +
    #  stat_summary(fun.y = mean, geom = "bar", fill = "White", colour = "Black")

    scatter <- ggplot(la16, aes(s_intrust, dictadura, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ study) +
    labs(x = "Institutional trust", y = "Support to dictatorship", colour = "country") 
````


## Institutional trust on civic knowledge

```{r , eval=TRUE, echo=TRUE, warning=FALSE, tidy=TRUE}    
    #ggplot(la16, aes(x=study, y=s_intrust)) +
    #  facet_wrap(~ country) +
    #  stat_summary(fun.y = mean, geom = "bar", fill = "White", colour = "Black")

    scatter <- ggplot(la16, aes(s_intrust, pv1civ, colour = factor(country))) 
    scatter + geom_smooth(method = "lm", alpha = 0.1) + 
      facet_wrap(~ study) +
    labs(x = "Civic knowledge", y = "Institutional trust", colour = "country") 
````


```{r , eval=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'} 
## Models that check hypotheses by country (PERU)
    peru=la16 %>%
      filter(country=="PER")
   
## Model1 for Peru: Support to dictatorships on civic knowledge and University Education
    per1= lmer(dictadura ~ univ + pv1civ + (1 | idschool), weights=totwgts, data=peru)
    #summary(per1)

## Model2 for Peru: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)    
    per2= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=peru)
    #summary(per2)
 
## Model2 for Peru: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government) + Institutional trust  
    per3= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + s_intrust + (1 | idschool), weights=totwgts, data=peru)
    #summary(per3)
    
## Model4 for Peru: Institutional trust on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)  
    per4= lmer(s_intrust ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=peru)

texreg(c(per1, per2, per3))
texreg(c(per4))
````


```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
#mediate(dictadura ~ civic200 + (s_intrust), data = peru, n.iter = 10000) %>%
#    print(short = FALSE)
    #help(mediate)

````


```{r , eval=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'} 
## Models that check hypotheses by country (MEXICO)
    mex=la16 %>%
      filter(country=="MEX")
   
## Model1 for Mexico: Support to dictatorships on civic knowledge and University Education
    mex1= lmer(dictadura ~ univ + pv1civ + (1 | idschool), weights=totwgts, data=mex)
    #summary(per1)

## Model2 for Mexico: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)    
    mex2= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=mex)
    #summary(per2)
 
## Model2 for Mexico: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government) + Institutional trust  
    mex3= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + s_intrust + (1 | idschool), weights=totwgts, data=mex)
    #summary(per3)
    
## Model4 for Mexico: Institutional trust on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)  
    mex4= lmer(s_intrust ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=mex)

texreg(c(mex1, mex2, mex3))
texreg(c(mex4))
````


```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
#mediate(dictadura ~ civic200 + (s_intrust), data = mex, n.iter = 10000) %>%
#    print(short = FALSE)
    #help(mediate)

````


```{r , eval=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'} 
## Models that check hypotheses by country (COLOMBIA)
    col=la16 %>%
      filter(country=="COL")
   
## Model1 for Chile: Support to dictatorships on civic knowledge and University Education
    col1= lmer(dictadura ~ univ + pv1civ + (1 | idschool), weights=totwgts, data=col)
    #summary(per1)

## Model2 for Chile: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)    
    col2= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=col)
    #summary(per2)
 
## Model2 for Chile: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government) + Institutional trust  
    col3= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + s_intrust + (1 | idschool), weights=totwgts, data=col)
    #summary(per3)
    
## Model4 for Chile: Institutional trust on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)  
    col4= lmer(s_intrust ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=col)

texreg(c(col1, col2, col3))
texreg(c(col4))
````


```{r , eval=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
#mediate(dictadura ~ civic200 + (s_intrust), data = col, n.iter = 10000) %>%
#    print(short = FALSE)
    #help(mediate)

````


```{r , eval=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'} 
## Models that check hypotheses by country (REP. DOMINICANA)
    gua=la16 %>%
      filter(country=="DOM")
   
## Model1 for Chile: Support to dictatorships on civic knowledge and University Education
    gua1= lmer(dictadura ~ univ + pv1civ + (1 | idschool), weights=totwgts, data=gua)
    #summary(per1)

## Model2 for Chile: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)    
    gua2= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=gua)
    #summary(per2)
 
## Model2 for Chile: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government) + Institutional trust  
    gua3= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + s_intrust + (1 | idschool), weights=totwgts, data=gua)
    #summary(per3)
    
## Model4 for Chile: Institutional trust on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)  
    gua4= lmer(s_intrust ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=gua)

texreg(c(gua1, gua2, gua3))
texreg(c(gua4))
````


```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
#mediate(dictadura ~ civic200 + (s_intrust), data = chile, n.iter = 10000) %>%
#    print(short = FALSE)
    #help(mediate)

````


```{r , eval=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'} 
## Models that check hypotheses by country (CHILE)
    chile=la16 %>%
      filter(country=="CHL")
   
## Model1 for Chile: Support to dictatorships on civic knowledge and University Education
    chl1= lmer(dictadura ~ univ + pv1civ + (1 | idschool), weights=totwgts, data=chile)
    #summary(per1)

## Model2 for Chile: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)    
    chl2= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=chile)
    #summary(per2)
 
## Model2 for Chile: Support to dictatorships on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government) + Institutional trust  
    chl3= lmer(dictadura ~ univ + pv1civ + pituto + prensa + police + cortes + s_intrust + (1 | idschool), weights=totwgts, data=chile)
    #summary(per3)
    
## Model4 for Chile: Institutional trust on civic knowledge, University Education and Good or Bad aspects for democracy (contract friends, press concentration, police arrest and courts influence government)  
    chl4= lmer(s_intrust ~ univ + pv1civ + pituto + prensa + police + cortes + (1 | idschool), weights=totwgts, data=chile)

texreg(c(chl1, chl2, chl3))
texreg(c(chl4))
````

## Models that check hypotheses by country (CHILE)
```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
 chile=la16 %>%
      filter(country=="CHL")

 pathmodel <- mplusObject(
   TITLE = "Path Model;",
   VARIABLE=" 
  cluster = jkreps; 
  Stratification = jkzones;
  Weight = totwgts;",
   ANALYSIS=
  "type = complex;",
   MODEL = "
     dictadura ON pv1civ pituto prensa police cortes
                  s_intrust
                  ;
     s_intrust ON pv1civ pituto prensa police cortes
                  ;
   MODEL INDIRECT:
     dictadura ind pv1civ;
   ",
   OUTPUT = "CINTERVAL;",
   rdata = chile)

fit <- mplusModeler(pathmodel, modelout = "modelChile.inp", run = 1L)
````

```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='markup'}
screenreg(fit, summaries = c("Observations"), digits = 3)

readModels("C:/Users/DANIEL/Dropbox (Personal)/notacoes/modelchile.out", recursive = FALSE, what = "indirect" )
````

## Models that check hypotheses by country (PERU)
```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
 peru=la16 %>%
      filter(country=="PER")

 pathmodel <- mplusObject(
   TITLE = "Path Model;",
   VARIABLE=" 
  cluster = jkreps; 
  Stratification = jkzones;
  Weight = totwgts;",
   ANALYSIS=
  "type = complex;",
   MODEL = "
     dictadura ON pv1civ pituto prensa police cortes
                  s_intrust
                  ;
     s_intrust ON pv1civ pituto prensa police cortes
                  ;
   MODEL INDIRECT:
     dictadura ind pv1civ;
   ",
   OUTPUT = "CINTERVAL;",
   rdata = peru)

fit <- mplusModeler(pathmodel, modelout = "modelperu.inp", run = 1L)
````

```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='markup'}
screenreg(fit, summaries = c("Observations"), digits = 3)

readModels("C:/Users/DANIEL/Dropbox (Personal)/notacoes/modelperu.out", recursive = FALSE, what = "indirect" )
````

## Models that check hypotheses by country (MEXICO)
```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
 mex=la16 %>%
      filter(country=="MEX")

 pathmodel <- mplusObject(
   TITLE = "Path Model;",
   VARIABLE=" 
  cluster = jkreps; 
  Stratification = jkzones;
  Weight = totwgts;",
   ANALYSIS=
  "type = complex;",
   MODEL = "
     dictadura ON pv1civ pituto prensa police cortes
                  s_intrust
                  ;
     s_intrust ON pv1civ pituto prensa police cortes
                  ;
   MODEL INDIRECT:
     dictadura ind pv1civ;
   ",
   OUTPUT = "CINTERVAL;",
   rdata = mex)

fit <- mplusModeler(pathmodel, modelout = "modelmex.inp", run = 1L)
````

```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='markup'}
screenreg(fit, summaries = c("Observations"), digits = 3)

readModels("C:/Users/DANIEL/Dropbox (Personal)/notacoes/modelmex.out", recursive = FALSE, what = "indirect" )
````

## Models that check hypotheses by country (DOMINICANA)
```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
 dom=la16 %>%
      filter(country=="DOM")

 pathmodel <- mplusObject(
   TITLE = "Path Model;",
   VARIABLE=" 
  cluster = jkreps; 
  Stratification = jkzones;
  Weight = totwgts;",
   ANALYSIS=
  "type = complex;",
   MODEL = "
     dictadura ON pv1civ pituto prensa police cortes
                  s_intrust
                  ;
     s_intrust ON pv1civ pituto prensa police cortes
                  ;
   MODEL INDIRECT:
     dictadura ind pv1civ;
   ",
   OUTPUT = "CINTERVAL;",
   rdata = dom)

fit <- mplusModeler(pathmodel, modelout = "modeldom.inp", run = 1L)
````

```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='markup'}
screenreg(fit, summaries = c("Observations"), digits = 3)

readModels("C:/Users/DANIEL/Dropbox (Personal)/notacoes/modeldom.out", recursive = FALSE, what = "indirect" )
````

## Models that check hypotheses by country (COLOMBIA)
```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
 col=la16 %>%
      filter(country=="COL")

 pathmodel <- mplusObject(
   TITLE = "Path Model;",
   VARIABLE=" 
  cluster = jkreps; 
  Stratification = jkzones;
  Weight = totwgts;",
   ANALYSIS=
  "type = complex;",
   MODEL = "
     dictadura ON pv1civ pituto prensa police cortes
                  s_intrust
                  ;
     s_intrust ON pv1civ pituto prensa police cortes
                  ;
   MODEL INDIRECT:
     dictadura ind pv1civ;
   ",
   OUTPUT = "CINTERVAL;",
   rdata = col)

fit <- mplusModeler(pathmodel, modelout = "modelcol.inp", run = 1L)
````

```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='markup'}
screenreg(fit, summaries = c("Observations"), digits = 3)

readModels("C:/Users/DANIEL/Dropbox (Personal)/notacoes/modelcol.out", recursive = FALSE, what = "indirect" )
````


## Models that check hypotheses by country (COLOMBIA)DUMMY
```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='asis'}
 col=la16 %>%
      filter(country=="COL")

 pathmodel <- mplusObject(
   TITLE = "Path Model;",
   VARIABLE=" 
  cluster = jkreps; 
  Stratification = jkzones;
  Weight = totwgts;
  categorical = dicdum;",
   ANALYSIS=
  "type = complex;",
   MODEL = "
     dicdum ON pv1civ pituto prensa police cortes
                  s_intrust
                  ;
     s_intrust ON pv1civ pituto prensa police cortes
                  ;
   MODEL INDIRECT:
     dicdum ind pv1civ;
   ",
   OUTPUT = "CINTERVAL;",
   rdata = col)

fit <- mplusModeler(pathmodel, modelout = "modelcol.inp", run = 1L)
````

```{r , eval=TRUE, echo=FALSE, warning=FALSE, tidy=TRUE, results='markup'}
screenreg(fit, summaries = c("Observations"), digits = 3)

readModels("C:/Users/DANIEL/Dropbox (Personal)/notacoes/modelcol.out", recursive = FALSE, what = "indirect" )
````
